---
title: "Homework 3"
output: github_document
---

```{r}
library(tidyverse)
library(patchwork)
```

```{r setup}

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1 

```{r}
library(p8105.datasets)
data("instacart")
```

The dataset contains information on Instacart Online Grocery Shopping in 2017. The variables `r variable.names(instacart)` are included in this data set. 
This dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns. 

How many aisles, and which are most common items from? 

```{r}
instacart %>%
count(aisle) %>%
  arrange (desc(n))

```

There are 134 aisles in the data set and The most popular aisles are fresh vegetables, fresh fruits, and packaged vegetables fruits. 

```{r}
instacart %>%
  count(aisle) %>% 
  filter(n> 10000) %>% 
  mutate(
    aisle = factor(aisle),
    aisle = fct_reorder(aisle, n)
  ) %>%
  ggplot(aes(x=aisle, y=n)) +
  geom_point() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust =1))
```

Let's make a table

```{r}
instacart %>% 
	filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
	group_by(aisle) %>% 
	count(product_name) %>% 
	mutate(rank = min_rank(desc(n))) %>% 
	filter(rank < 4) %>% 
	arrange(aisle, rank) %>% 
	knitr::kable()
```

Apples vs Ice cream

```{r}
instacart %>% 
	filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
	group_by(product_name, order_dow) %>% 
	summarize(mean_hour = mean(order_hour_of_day)) %>% 
	pivot_wider(
		names_from = order_dow,
		values_from = mean_hour
	)
```



## Problem 2

```{r}
accel_df = 
read.csv("./data/accel_data.csv") %>%
  janitor::clean_names() %>%
    pivot_longer(
      activity_1:activity_1440, 
      names_to = "activity_minute", 
      names_prefix = "activity_", 
      values_to ="activity_count"
      ) %>%
  
mutate (
  day = factor(day), 
  day = forcats::fct_relevel(day, c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))) %>%
    
 mutate(weekend_weekday=day) %>%

mutate(weekend_weekday = recode(weekend_weekday, Sunday = "Weekend", Saturday = "Weekend", Friday = "Weekday",Thursday = "Weekday", Wednesday = "Weekday", Tuesday = "Weekday", Monday = "Weekday")) %>%
  mutate(
     activity_minute = as.numeric(activity_minute))


```


This data set contains 4 numeric and 1 character variable. 

```{r}
accel_df  %>%
  group_by(day, week) %>%
  summarize (total_activity = sum(activity_count)) %>%
  pivot_wider(
    names_from = day, 
    values_from = total_activity
  )  %>%
  	knitr::kable()


```


```{r}
accel_df  %>%
  ggplot(aes(x= activity_minute, y = activity_count, group = day_id,color=day)) + 
  geom_line(alpha = .2) +
  geom_smooth(aes(group = day)) 

```

## Problem 3

```{r}
library(p8105.datasets)
data("ny_noaa")
```

```{r}
ny_noaa = ny_noaa %>%
  separate(date, into = c("year", "month", "day"), convert = TRUE)%>%
  mutate(prcp = as.numeric(prcp), 
         snow = as.numeric(snow), 
          snwd = as.numeric(snwd), 
    tmin = as.numeric(tmin), 
   tmax = as.numeric(tmax),
   month = as.factor(month)
   ) 
```

The most common observed value for snowfall is `r summarize(ny_noaa, mean(snow))` 

```{r}
ny_noaa = ny_noaa  %>%
  group_by(id, year, month) %>%
  filter(month == 1|month == 7 ) %>%
  summarize(mean_tmax = mean(tmax, na.rm = TRUE, color=id)) %>%
  ggplot(aes(x = year, y = mean_tmax, group = id)) + 
  geom_point() +
  geom_path (alpha =.05, size = .3)+
  facet_grid(~month) +
   theme(legend.position = "bottom")

```


