---
title: "Homework 3"
output: github_document
---

```{r setup}
library(tidyverse)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1 

```{r}
library(p8105.datasets)
data("instacart")
```

The dataset contains information on Instacart Online Grocery Shopping in 2017. The variables `r variable.names(instacart)` are included in this data set. 
This dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns. 

How many aisles, and which are most common items from? 

```{r}
instacart %>%
count(aisle) %>%
  arrange (desc(n))

```

There are 134 aisles in the data set and The most popular aisles are fresh vegetables, fresh fruits, and packaged vegetables fruits. 

```{r}
instacart %>%
  count(aisle) %>% 
  filter(n> 10000) %>% 
  mutate(
    aisle = factor(aisle),
    aisle = fct_reorder(aisle, n)
  ) %>%
  ggplot(aes(x=aisle, y=n)) +
  geom_point() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust =1))
```

Let's make a table

```{r}
instacart %>% 
	filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
	group_by(aisle) %>% 
	count(product_name) %>% 
	mutate(rank = min_rank(desc(n))) %>% 
	filter(rank < 4) %>% 
	arrange(aisle, rank) %>% 
	knitr::kable()
```

Apples vs Ice cream

```{r}
instacart %>% 
	filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
	group_by(product_name, order_dow) %>% 
	summarize(mean_hour = mean(order_hour_of_day)) %>% 
	pivot_wider(
		names_from = order_dow,
		values_from = mean_hour
	)
```

